Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 longoutput.tex
Add notes on notation

After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate.

@@

Then, we ensure that the initial condition is set up correctly. Let $n$ be the number of the qubits in the circuit.
$$H_{in}=\sum_i^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
Where $x_i$ is the $i$th bit of $x$. The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, this can be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates as
$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$

@@

\subsection{2-local ZX Hamiltonians}

We then follow \cite{biamonte_love_2008} in writing each terms of $H$ into only $Z$ and $X$ measurements...

This probably involves some kind of basis arguments on the Hamiltonians and maybe some stuff that's a bit more ugly. This should not change the state. I'll have to write this out later...

>>>>

After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate. Let $x_i$ denote the $i$th bit of $x$, and $|x|$ denote the number of the qubits in the circuit.

@@

Then, we ensure that the initial condition is set up correctly.
$$H_{in}=\sum_i^{|x|}(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, this can be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates as
$$H_{in}=\frac{1}{4}\sum_{i=1}^{|x|}(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$

@@

TODO Write down the final Hamiltonian. Possibly also the eigenvalue gap.
